Comparison with Christensen paper

### 2018-12-27 paper-comparison/compare-christensen.Rmd
Files for side by side comparison of paper changepoint
Paper changepoint on paper lda vs LDATS lda.

At this point I find it easiest to open the image files in 'paper-changepoint-files' and put the LDATS lda ones side by side with the paper lda ones. I know this is... not ideal.

Both give same #'s of changepoints (4 or 6 - 6 has lower deviance, but I'm not sure if the changepoint is to be trusted for 6 cpts?) and roughly the same locations.

The LDATs LDA w/ 4 cpts has less bimodality in the 1990's  than the paper LDA.

#### run LDATS LDA with LDATS changepoint
```{r, include = F}
# remove paper LDA (for memory)
rm(ldamodel)
```

@@

@@

>>>>

#### run LDATS LDA with LDATS changepoint

@@

```{r paper paper selection}
ntopics = ldamodel@k
# Load models and compare deviance to select the best one
load('/Users/renatadiaz/Documents/model-stash/paper_cpt_paper_lda1.Rds')
load('/Users/renatadiaz/Documents/model-stash/paper_cpt_paper_lda2.Rds')
load('/Users/renatadiaz/Documents/model-stash/paper_cpt_paper_lda3.Rds')
load('/Users/renatadiaz/Documents/model-stash/paper_cpt_paper_lda4.Rds')
load('/Users/renatadiaz/Documents/model-stash/paper_cpt_paper_lda5.Rds')
load('/Users/renatadiaz/Documents/model-stash/paper_cpt_paper_lda6.Rds')

# change point model selection
# mean deviance ( -2 * log likelihood) + 2*(#parameters)
mean(cp_results_rodent$saved_lls * -2) + 2*(3*(ntopics-1)*(1+1)+(1))
mean(cp_results_rodent2$saved_lls * -2)+ 2*(3*(ntopics-1)*(2+1)+(2))
mean(cp_results_rodent3$saved_lls * -2)+ 2*(3*(ntopics-1)*(3+1)+(3))
mean(cp_results_rodent4$saved_lls * -2)+ 2*(3*(ntopics-1)*(4+1)+(4))
mean(cp_results_rodent5$saved_lls * -2)+ 2*(3*(ntopics-1)*(5+1)+(5))
mean(cp_results_rodent6$saved_lls * -2)+ 2*(3*(ntopics-1)*(5+1)+(5))

@@

### Compare model outcomes
